# ISS Big Data Analytics Report

## Dataset : “Climate Change: Earth Surface Temperature Data”

**Importing Libraries and setting working directory**
```{r, message = F, warning=F}
library(data.table)
library(ggplot2)
library(ggfortify)
library(dplyr)
library(reshape2)
library(viridis)

#setwd("~/Desktop/class/9/big_data/input")

```

**1. Loading temprature data by country **
**2. Tuning the date field to the required format**
**3. Removing the NA's **

```{r, message = F, warning=F}

world_temp = fread("climate-change-earth-surface-temperature-data/GlobalLandTemperaturesByCountry.csv")
world_temp$date = as.Date(world_temp$dt, "%Y-%m-%d")
world_temp$month = month(world_temp$date)
world_temp$year = year(world_temp$date)
world_temp = world_temp[!is.na(AverageTemperature),]
head(world_temp)

```

**1. Exploring the temperature by month & year - to cross verify across seasons **
**2. Selecting random set of countries for analysis**

```{r}
# extracting world's average temperature month-wise & year-wise
world_temp_2 = world_temp %>%
  group_by(year, month, Country, date) %>%
  summarise(avg_Temp = mean(AverageTemperature))

print(world_temp_2)

Main_country <- c("China", "United States", "France", "Japan","Germany", "India","United Kingdom", "Italy", "Brazil", "Canada")
Main_temp <- world_temp_2 %>% filter(Country %in% Main_country)
print(Main_temp)
```

**Plotting multiple graphs to answer questions to solve our hypothesis**

**Question 1: How is the temperature variation of the selected countries during a year?**

```{R}
ggplot(Main_temp, aes(x = month, y = avg_Temp, color= Country, fill=Country)) +geom_smooth()+labs(    
    x = "Month",    
    y = "Average Temperature",    
    title = "Trend of temperature during the year",    
    caption = "Temperature change analysis"  )

```

**Question 2: How is the change in temperature of the selected countries during the last 300 years?**
```{R}

ggplot(Main_temp, aes(x = year, y =avg_Temp, color= Country, fill=Country)) +geom_smooth()+labs(    
    x = "Year",    
    y = "Average Temperature",    
    title = "Changes in temperature over the past two hundred years",    
    caption = "Temperature change analysis"  )
```

**Question 3: How can we relate the trend in temperature change of those selected countries to the global temperature change?**

```{R}

ggplot(Main_temp, aes(x = year, y = avg_Temp))+geom_smooth()+labs(    
    x = "Year",    
    y = "Average Temperature",    
    title = "Temperature Trend of The World",    
    caption = "Temperature change analysis"  )


ff <- filter(Main_temp, Country %in% c("Japan"))
ggplot(ff,  aes(x = year, y=avg_Temp, color= Country)) + geom_smooth(method="loess")+labs(    
    x = "Year",    
    y = "Average Temperature",    
    title = "Temperature Trend of Japan",    
    caption = "Temperature change analysis"  )

```

**Question 4: What is the rate of change in global temperature based on data from the last few decades? **


```{R}
print("calculating")
country_temp = world_temp %>%   #将这一步的结果直接作为下一步的第一个参数
  group_by(Country, year) %>%
  summarise(med_Temp = median(AverageTemperature)) %>%
  filter(year == 1950 | year == 2013)
print(country_temp)
# converting data to wide format
print("converting")
country_temp_wide = dcast(country_temp, formula = Country ~ year)

# denoting a country with '1' if the temperature increased during 1950-2013 and '0' otherwise
print("denoting")
country_temp_wide$temp_incrs_flag = ifelse(country_temp_wide$`2013` > country_temp_wide$`1950`,1,0)
country_temp_wide$change=country_temp_wide$`2013`-country_temp_wide$`1950`
print(country_temp_wide)


### add a map showing countries with increase and decrease in temp ###
print("add")
map = map_data("world") # map_data() is a ggplot function
unique_country_temp = data.frame(region = country_temp_wide$Country, temp_increased = country_temp_wide$temp_incrs_flag, change=country_temp_wide$change)

# fetching desired data to 'map' dataframe
print("fetching")
map = left_join(map, unique_country_temp) 

missed_countries = c("Antigua","Bosnia and Herzegovina","Republic of Congo",
                     "Curacao", "Falkland Islands", "UK","Heard Island",
                     "Saint Kitts","Myanmar", "Bonaire", "South Sudan", "South Georgia",
                     "Sao Tome and Principe", "Timor-Leste", "Tobago", "Saint Vincent",
                     "French Southern and Antarctic Lands", "Barbuda", "Saint Barthelemy",
                     "Democratic Republic of the Congo","Guinea-Bissau",
                     "Palestine","Saint Pierre and Miquelon", "Turks and Caicos Islands",
                     "Trinidad","USA")

print(map)

map$temp_increased = ifelse(map$region %in% missed_countries, 0, map$temp_increased)
map = map[!is.na(map$temp_increased),]

```

```{R}
# to draw the pic of World temperature change from 1950 to 2013
ggplot(map)+geom_polygon(aes(x = long, y = lat, group = group, fill = map$change)) + 
scale_fill_gradient2(limits=c(-10,10),low = 'blue',  high = 'red') +labs(    
    title = "World temperature change from 1950 to 2013",    
    caption = "Temperature change analysis"  )

```

**Using Sub-dataset - GlobalTemperatures to verify the growing temperature trends""**

```{r, message = F, warning=F}

data_global = fread("climate-change-earth-surface-temperature-data/GlobalTemperatures.csv")
data_global$year <- as.Date(data_global$dt,format="%Y")

#converting the dt variable to date
data_global$dt<-as.Date(data_global$dt,format="YYYY")
tail(data_global)

# Filtering the data with average temperate above 6.5 and summarising the data without NA's
data_world <- data_global%>%group_by(year)%>%summarize(Avg_Temp=mean(LandAverageTemperature,na.rm=T))%>%filter(Avg_Temp>6.5)
data_world$year <- as.numeric(data_world$year)

#Printing the plot to visualise the increase in global average temperature
ggplot(data_world, aes(x=year, y=Avg_Temp,color=Avg_Temp))+
  geom_point()+
  scale_color_viridis(option = "D")+
  ggtitle("Increasing Global Average Temperature - Land")+
  scale_x_discrete(label="")


```
